The state learner \\ {-- a super learner for right-censored data}

### 2023-11-21 tex/state-learner-pub-version.tex
simulation studies

The problem with most existing super learners for right-censored data is that
they depend on a pre-specified estimator of the censoring distribution. The main
idea of the state learner is to jointly use learners of \( \Lambda_1 \),
\( \Lambda_2 \), and \( \Gamma \), and the relations in
equation~(\ref{eq:parametrizeP}), to learn a feature of the observed data
distribution \( P \). The discrete state learner ranks a tuple of learners of
\( (\Lambda_1, \Lambda_2, \Gamma) \) based on how well they jointly model the
observed data. To formally introduce the state learner, we define the
multi-state process
\begin{equation*}
  \eta(t) = \1\{\tilde{T} \leq t, \tilde D=1\} + 2\,\1\{\tilde{T} \leq t, \tilde D=2\}+ 3\,\1\{\tilde{T} \leq t, \tilde D=0\},
  \quad \text{for} \quad t \in [0, \tau].
\end{equation*}
Note that at time \(t\), we observe that each observation is in one of four
mutually exclusive states (Figure \ref{fig:multi-state-process}).
\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{./figures/figure-multi-state-process.pdf}
  \caption{Illustration of the multi-state process \(\eta\) used by
    the state learner. Note that `censored' is a state, hence the
    process is always observed at any time.}
  \label{fig:multi-state-process}
\end{figure}
The conditional distribution of \( \eta(t) \) given \( X=x \) is
determined by the function
\begin{equation}
  \label{eq:F-def}
  F(t, k, x) = P(\eta(t) = k \mid X=x),
  \quad \text{for all} \quad
  t \in [0,\tau],
  k \in \{0,1,2,3\},
  x \in \mathcal{X}.
\end{equation}
The function \( F \) describes the conditional state occupation
probabilities corresponding to the observed multi-state process
\(\eta\).

@@

An example of a targeted estimator is the \fxnote*{also TMLE, depending on
  implementation}{one-step estimator}, defined as
\begin{equation}
    \label{eq:one-step-def}
    \hat{\Psi}_{\text{OS}}(\data_n)
    =
    \tilde{\Psi}^0(\hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
    H(\data_n))
    + \empmeas{[\psi(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
      \hat{b}_n(\data_n) )]},
\end{equation}
where \( \empmeas \) is the empirical measure of a sample \(\{O_i\}_{i=1}^n\).
We can make the following asymptotic expansion of the one-step estimator
\citep{pfanzagl1985contributions,fisher2021visually,kennedy2022semiparametric},
\begin{equation*}
  \hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)
  =  \empmeas{[\psi(\blank ; \Lambda_1, \Lambda_2, \Gamma)]}
  +\mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)} + \smallO_{P}(n^{-1/2}),
\end{equation*}
where the remainder term is typically such that
\citep{van2003unified,rytgaard2022continuous}
\begin{equation}
  \label{eq:4}
  \mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)}
  = \mathcal{O}_P{
    \left\{
      (\Lambda_1-\hat{\Lambda}_{1,n})^2
      +
      (\Lambda_2-\hat{\Lambda}_{2,n})^2
      +
      (\Gamma-\hat{\Gamma}_{n})^2
    \right\}
  }.
\end{equation}
Hence, under a suitable Donsker class regularity condition
\citep{bickel1993efficient,kennedy2016semiparametric}, when
equation~(\ref{eq:4}) holds and the nuisance parameters $\Lambda_1$,
$\Lambda_2$, and $\Gamma$ are consistently estimated at rate
\( \smallO_P{(n^{-1/4})} \) then
\begin{equation}
  \label{eq:3}
  \sqrt{n}(\hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)) \weakly \mathcal{N}(0,
  P{[\psi(\blank; \Lambda_1, \Lambda_2, \Gamma)^2]}).
\end{equation}
In particular, equation~(\ref{eq:3}) and Slutsky's lemma imply that we can
obtain asymptotically valid \((1-\alpha)\cdot100\%\) confidence intervals by
calculating
\begin{equation*}
  \left[
    \hat{\Psi}_{\text{OS}}(\data_n) - q_{\alpha/2} \hat{\sigma}(\data_n) ,
    \;
    \hat{\Psi}_{\text{OS}}(\data_n) + q_{\alpha/2} \hat{\sigma}(\data_n)
  \right],
\end{equation*}
where \( q_{\alpha} \) is the \( (1-\alpha) \)-quantile or the standard normal
distribution, and
\begin{equation*}
  \hat{\sigma}(\data_n) = 
  \left(
    \empmeas{
      \left[
        \psi(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n))^2
      \right]}
  \right)^{1/2}.
\end{equation*}

@@

Using equation~(\ref{eq:surv-def}), we may write
\( \theta_{{\tau}}(Q) = \tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu) \),
where
\begin{equation}
  \label{eq:1}    
  \begin{split}
  \tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu) & =
  \int_{\mathcal{W}} 
  \int_0^{\tau}
  e^{-\Lambda_1(s- \mid w, 1)-\Lambda_2(s- \mid w, 1)}  \Lambda_1(\diff s \mid
  w, 1)
  \mu(\diff w)
  \\
  &  \quad
  -\int_{\mathcal{W}} 
  \int_0^{\tau}
  e^{-\Lambda_1(s- \mid w, 0)-\Lambda_2(s- \mid w, 0)}  \Lambda_1(\diff s \mid w, 0)
  \mu(\diff w).
  \end{split}
\end{equation}
The efficient influence function for the parameter $\tilde{\Psi}_{\tau}$
depends on the set \( (\Lambda_1, \Lambda_2, \Gamma, \pi) \) of nuisance
parameters, and is given by \fxnote*{other refs?}{\citep{rytgaard2022targeted}}
\begin{equation}
  \label{eq:5}
  \begin{split}
    & \psi_{\tau}(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
    \\
    & =
      \sum_{l=1}^{2} \int_0^{\tau}
      \left[
      h_{\tau,l,1}(t, O  ; \Lambda_1, \Lambda_2, \Gamma, \pi)
      - h_{\tau,l,0}(t, O  ; \Lambda_1, \Lambda_2, \Gamma, \pi)
      \right]
    \\
    & \quad\qquad  \qquad
      \times
      \left(
      N_l(\diff t) - \1{\{\tilde{T} \geq t\}}\Lambda_l(\diff t \mid A, W)
      \right)
    \\
    & \quad
      -\sum_{a=0}^{1} 
      \left\{
      (-1)^a
      \int_0^{\tau}
      e^{-\Lambda_1(s- \mid W, a)-\Lambda_2(s- \mid W, a)}  \Lambda_1(\diff s \mid
      W, a)
      \right\}
      - \tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu),
    % & \quad+ \int_0^{\tau} e^{-\Lambda_1(s- \mid W, 1)-\Lambda_2(s- \mid W,
    % 1)} \Lambda_1(\diff s \mid W, 1)
    % \\
    % & \quad - \int_0^{\tau} e^{-\Lambda_1(s- \mid W, 0)-\Lambda_2(s- \mid W,
    % 0)} \Lambda_1(\diff s \mid W, 0)
  \end{split}
\end{equation}
where
\begin{align*}
  h_{\tau,l,a}(t, O  ; \Lambda_1, \Lambda_2, \Gamma, \pi)
  =&  \frac{\1{\{A=a\}} e^{\Gamma(t-\mid A, W)}}{\pi(W)^{a}(1-\pi(W))^{1-a}}
  \\
   & \quad \times
     \left(
     1- \frac{\int_t^{\tau} e^{-\Lambda_1(s- \mid A, W)-\Lambda_2(s- \mid A, W)}
     \Lambda_1(\diff s \mid A, W)}
     {e^{-\Lambda_1(t \mid A, W)-\Lambda_2(t \mid A, W)}}
     \right)^{\1{\{l=1\}}}
  \\
   & \quad\times
     \left(
     - \frac{\int_t^{\tau} e^{-\Lambda_1(s- \mid A, W)-\Lambda_2(s- \mid A, W)}
     \Lambda_1(\diff s \mid A, W)}
     {e^{-\Lambda_1(t \mid A, W)-\Lambda_2(t \mid A, W)}}
     \right)^{\1{\{l=2\}}}
\end{align*}
Equation~(\ref{eq:1}) and~(\ref{eq:5}) then allow us to construct a one-step
estimator by using the definition given in equation~(\ref{eq:one-step-def}),
which gives the estimator
\begin{equation}
  \label{eq:one-step-comp-ate}
  \tilde{\Psi}_{t, j}^0(\hat{a}_1(\data_n), \hat{a}_2(\data_n), \hat{\mu}_n(\data_n))
\end{equation}

@@

@@

\begin{figure}
  \centerline{\includegraphics[width=1\linewidth]{./figures/ipcw-fail.pdf}}
  \caption[]{Results for scenario~1 of the simulation study. For the learner
    selected by each of the four discrete super learners, the Brier score
    calculated in a large independent data set without censoring is plotted
    against sample size. The results are based on 200 repetitions.}
  \label{fig:ipcw-fail}
\end{figure}

@@

The results are shown in Figure~\ref{fig:zelefski}. We see that the Brier score
of the IPCW super learner based on a misspecified censoring model (IPCW(KM))
decreased with sample size, but is larger than that of the other super learners
for all sample sizes. The state learner and the IPCW super learner based on a
correctly pre-specified censoring model demonstrate similar performance for all
sample sizes. The performance of both the IPCW(Cox) super learner and the state
learner approaches the benchmark provided by the oracle selector for large sample
sizes.
\begin{figure}
  \centerline{\includegraphics[width=1\linewidth]{./figures/zelefski-sim.pdf}}
  \caption[]{Results for scenario~2 of the simulation study. For the learner
    selected by each of the four discrete super learners, the Brier score
    calculated in a large independent data set without censoring is plotted
    against sample size. The results are based on 200 repetitions.}
  \label{fig:zelefski}
\end{figure}

@@

\begin{figure}
  \centerline{\includegraphics[width=1\linewidth]{./figures/zelefski-real-data.pdf}}
  \caption[]{The results of applying the 125 combinations of learners to the
    prostate cancer data set. The learners are \texttt{KM} (KM), \texttt{Cox
      strata CS} (strata), \texttt{Lasso} (lasso), \texttt{Elastic} (elastic),
    and \texttt{RF} (RF) as described Table~\ref{tab:zel-library}. The error
    bars are based on five repetitions using different splits. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Death learner', and `Censoring learner', respectively.}
  \label{fig:zelefski-real}
\end{figure}

\begin{table}[ht]
  \centering \input{./figures/zel-tab.tex}
  \caption{The 10 best performing models in terms of integrated Brier score. The
    reported standard errors are based on five repetitions using different
    splits. The models are described in Table~\ref{tab:zel-library}. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Death leaner', and `Censoring learner', respectively.}
  \label{tab:zelefski-real}
\end{table}
\section{Discussion}
\label{sec:discussion}

>>>>

The problem with most existing super learners for right-censored data is that
they depend on a pre-specified estimator of the censoring distribution. The main
idea of the state learner is to jointly use learners of \( \Lambda_1 \),
\( \Lambda_2 \), and \( \Gamma \), and the relations in
equation~(\ref{eq:parametrizeP}), to learn a feature of the observed data
distribution \( P \). The discrete state learner ranks a tuple of learners of
\( (\Lambda_1, \Lambda_2, \Gamma) \) based on how well they jointly model the
observed data. To formally introduce the state learner, we define the
multi-state process
\begin{equation*}
  \eta(t) = \1\{\tilde{T} \leq t, \tilde D=1\} + 2\,\1\{\tilde{T} \leq t, \tilde D=2\}+ 3\,\1\{\tilde{T} \leq t, \tilde D=0\},
  \quad \text{for} \quad t \in [0, \tau].
\end{equation*}
Note that at time \(t\), we observe that each observation is in one of four
mutually exclusive states (Figure \ref{fig:multi-state-process}).
\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{../figures/figure-multi-state-process.pdf}
  \caption{Illustration of the multi-state process \(\eta\) used by
    the state learner. Note that `censored' is a state, hence the
    process is always observed at any time.}
  \label{fig:multi-state-process}
\end{figure}
The conditional distribution of \( \eta(t) \) given \( X=x \) is
determined by the function
\begin{equation}
  \label{eq:F-def}
  F(t, k, x) = P(\eta(t) = k \mid X=x),
  \quad \text{for all} \quad
  t \in [0,\tau],
  k \in \{0,1,2,3\},
  x \in \mathcal{X}.
\end{equation}
The function \( F \) describes the conditional state occupation
probabilities corresponding to the observed multi-state process
\(\eta\).

@@

An example of a targeted estimator is the \fxnote*{also TMLE, depending on
  implementation}{one-step estimator}, defined as
\begin{equation}
    \label{eq:one-step-def}
    \hat{\Psi}_{\text{OS}}(\data_n)
    =
    \tilde{\Psi}^0(\hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
    H(\data_n))
    + \empmeas{[\psi(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
      \hat{b}_n(\data_n) )]},
\end{equation}
where \( \empmeas \) is the empirical measure of a sample \(\{O_i\}_{i=1}^n\).
We can make the following asymptotic expansion of the one-step estimator
\citep{pfanzagl1985contributions,van2003unified,fisher2021visually,kennedy2022semiparametric,rytgaard2022continuous},
\begin{equation*}
  \hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)
  =  \empmeas{[\psi(\blank ; \Lambda_1, \Lambda_2, \Gamma)]}
  +\mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)} + \smallO_{P}(n^{-1/2}),
\end{equation*}
where the remainder term is typically such that
\begin{equation}
  \label{eq:4}
  \mathrm{Rem}{(\hat{\Lambda}_{1,n},\hat{\Lambda}_{2,n},  \hat{\Gamma}_n, P)}
  = \mathcal{O}_P{
    \left\{
      (\Lambda_1-\hat{\Lambda}_{1,n})^2
      +
      (\Lambda_2-\hat{\Lambda}_{2,n})^2
      +
      (\Gamma-\hat{\Gamma}_{n})^2
    \right\}
  }.
\end{equation}
Hence, under a suitable Donsker class regularity condition
\citep{bickel1993efficient,kennedy2016semiparametric}, when
equation~(\ref{eq:4}) holds and the nuisance parameters $\Lambda_1$,
$\Lambda_2$, and $\Gamma$ are consistently estimated at rate
\( \smallO_P{(n^{-1/4})} \), then
\begin{equation}
  \label{eq:3}
  \sqrt{n}(\hat{\Psi}_{\text{OS}}(\data_n)- \Psi(P)) \weakly \mathcal{N}(0,
  P{[\psi(\blank; \Lambda_1, \Lambda_2, \Gamma)^2]}).
\end{equation}
In particular, equation~(\ref{eq:3}) and Slutsky's lemma imply that we can
obtain asymptotically valid \((1-\alpha)\cdot100\%\) confidence intervals by
calculating
\begin{equation*}
  \left[
    \hat{\Psi}_{\text{OS}}(\data_n) - q_{\alpha/2} \hat{\sigma}(\data_n) ,
    \;
    \hat{\Psi}_{\text{OS}}(\data_n) + q_{\alpha/2} \hat{\sigma}(\data_n)
  \right],
\end{equation*}
where \( q_{\alpha} \) is the \( (1-\alpha) \)-quantile or the standard normal
distribution, and
\begin{equation*}
  \hat{\sigma}(\data_n) = 
  \left(
    \empmeas{
      \left[
        \psi(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n))^2
      \right]}
  \right)^{1/2}.
\end{equation*}

@@

Using equation~(\ref{eq:surv-def}), we may write
\( \theta_{{\tau}}(Q) = \tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu) \),
where
\begin{equation}
  \label{eq:1}    
  \tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu) & =
  \int_{\mathcal{W}} 
  \int_0^{\tau}
  e^{-\Lambda_1(s- \mid w, 1)-\Lambda_2(s- \mid w, 1)}  \Lambda_1(\diff s \mid
  w, 1)
  \mu(\diff w)
  &  \quad
  -\int_{\mathcal{W}} 
  \int_0^{\tau}
  e^{-\Lambda_1(s- \mid w, 0)-\Lambda_2(s- \mid w, 0)}  \Lambda_1(\diff s \mid w, 0)
  \mu(\diff w).
The efficient influence function for the parameter $\tilde{\Psi}_{\tau}$ depends
on the set \( (\Lambda_1, \Lambda_2, \Gamma, \pi) \) of nuisance parameters.
% \begin{equation}
%   \label{eq:5}
%   \begin{split}
%     & \psi_{\tau}(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
%     \\
%     & =
%       \sum_{l=1}^{2} \int_0^{\tau}
%       \left[
%       h_{\tau,l,1}(t, O  ; \Lambda_1, \Lambda_2, \Gamma, \pi)
%       - h_{\tau,l,0}(t, O  ; \Lambda_1, \Lambda_2, \Gamma, \pi)
%       \right]
%     \\
%     & \quad\qquad  \qquad
%       \times
%       \left(
%       N_l(\diff t) - \1{\{\tilde{T} \geq t\}}\Lambda_l(\diff t \mid A, W)
%       \right)
%     \\
%     & \quad
%       -\sum_{a=0}^{1} 
%       \left\{
%       (-1)^a
%       \int_0^{\tau}
%       e^{-\Lambda_1(s- \mid W, a)-\Lambda_2(s- \mid W, a)}  \Lambda_1(\diff s \mid
%       W, a)
%       \right\}
%       - \tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu),
%     % & \quad+ \int_0^{\tau} e^{-\Lambda_1(s- \mid W, 1)-\Lambda_2(s- \mid W,
%     % 1)} \Lambda_1(\diff s \mid W, 1)
%     % \\
%     % & \quad - \int_0^{\tau} e^{-\Lambda_1(s- \mid W, 0)-\Lambda_2(s- \mid W,
%     % 0)} \Lambda_1(\diff s \mid W, 0)
%   \end{split}
% \end{equation}
% where
% \begin{align*}
%   h_{\tau,l,a}(t, O  ; \Lambda_1, \Lambda_2, \Gamma, \pi)
%   =&  \frac{\1{\{A=a\}} e^{\Gamma(t-\mid A, W)}}{\pi(W)^{a}(1-\pi(W))^{1-a}}
%   \\
%    & \quad \times
%      \left(
%      1- \frac{\int_t^{\tau} e^{-\Lambda_1(s- \mid A, W)-\Lambda_2(s- \mid A, W)}
%      \Lambda_1(\diff s \mid A, W)}
%      {e^{-\Lambda_1(t \mid A, W)-\Lambda_2(t \mid A, W)}}
%      \right)^{\1{\{l=1\}}}
%   \\
%    & \quad\times
%      \left(
%      - \frac{\int_t^{\tau} e^{-\Lambda_1(s- \mid A, W)-\Lambda_2(s- \mid A, W)}
%      \Lambda_1(\diff s \mid A, W)}
%      {e^{-\Lambda_1(t \mid A, W)-\Lambda_2(t \mid A, W)}}
%      \right)^{\1{\{l=2\}}}
% \end{align*}
Define the quantities
  \omega_a(A,W; \pi)
  &=  \frac{% (-1)^{a+1}
    \1{\{A=a\}}}{\pi(W)^{a}(1-\pi(W))^{1-a}},
  g(t, A, W; \Lambda_1, \Lambda_2)
  & = \int_0^{t}
    e^{-\Lambda_1(s- \mid W, A)-\Lambda_2(s- \mid W, A)}  \Lambda_1(\diff s \mid
    W, A),
  M_j(\diff t \mid A, W;  \Lambda_j  )
  & = N_j(\diff t) -
    \1{\{\tilde{T} \geq t\}} \Lambda_j(\diff t \mid W, A),
    \quad j \in \{1,2\},
  \intertext{and}
  M(\diff t \mid A, W;  \Lambda_1, \Lambda_2  )
  & = M_1(\diff t \mid A, W;  \Lambda_1  ) +
    M_2(\diff t \mid A, W;  \Lambda_2  ).
The efficient influence function can then be written as
\citep{van2003unified,jewell2007non,rytgaard2022targeted},
  \psi_{\tau}(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  = \psi_{\tau}^1(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  - \psi_{\tau}^0(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
  -\tilde{\Psi}_{t}^0(\Lambda_1, \Lambda_2, \mu),
where
\begin{equation}
  \label{eq:5}
    & \psi_{\tau}^a(O; \Lambda_1, \Lambda_2, \Gamma, \pi)
      \omega_a(A,W; \pi)
      \int_0^{\tau} e^{\Gamma(t- \mid A, W)}   
      M_1(\diff t \mid A, W; \Lambda_1)
    & \quad
      -
      \omega_a(A,W; \pi)
      g(\tau, A, W; \Lambda_1, \Lambda_2)
      \int_0^{\tau}
      e^{[\Gamma+\Lambda_1 + \Lambda_2](t- \mid A, W)}
      M(\diff t \mid A, W; \Lambda_1, \Lambda_2)
    & \quad
      +
      \omega_a(A,W; \pi)      
      \int_0^{\tau}
      g(t, A, W; \Lambda_1, \Lambda_2)
      e^{[\Gamma+\Lambda_1 + \Lambda_2](t- \mid A, W)}
      M(\diff t \mid A, W; \Lambda_1, \Lambda_2)
    & \quad + g(\tau, a, W; \Lambda_1, \Lambda_2).

Equations~(\ref{eq:1}) and~(\ref{eq:5}) allow us to construct a one-step
estimator by using the definition given in equation~(\ref{eq:one-step-def}),
which gives the estimator
\begin{equation}
  \label{eq:one-step-comp-ate}
  \begin{split}
    \hat{\Psi}_{t,\text{OS}}(\data_n)
    = &
        \tilde{\Psi}_{t}^0(\hat{a}_1(\data_n), \hat{a}_2(\data_n),
        \hat{\mu}_n(\data_n))
    \\
      &
        +
        \empmeas{[\psi_{\tau}(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
    \\
    = &
        \empmeas{[\psi_{\tau}^1(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
    \\
      &
        - \empmeas{[\psi_{\tau}^0(\blank; \hat{a}_{1,n}(\data_n), \hat{a}_{2,n}(\data_n),
        \hat{b}_n(\data_n), \hat{\pi}_n(\data_n))]}
  \end{split}
\end{equation}

@@

%% IPCW with potentially misspecified censoring model.
%%
%% Applying SL, concrete, and Westling on classical data set. (Where to put
%% this?)

@@

\begin{figure}
  \centerline{\includegraphics[width=1\linewidth]{../figures/ipcw-fail.pdf}}
  \caption[]{Results for scenario~1 of the simulation study. For the learner
    selected by each of the four discrete super learners, the Brier score
    calculated in a large independent data set without censoring is plotted
    against sample size. The results are based on 200 repetitions.}
  \label{fig:ipcw-fail}
\end{figure}

@@

The results are shown in Figure~\ref{fig:zelefski}. We see that the Brier score
of the IPCW super learner based on a misspecified censoring model (IPCW(KM))
decreased with sample size, but is larger than that of the other super learners
for all sample sizes. The state learner and the IPCW super learner based on a
correctly pre-specified censoring model demonstrate similar performance for all
sample sizes. The performance of both the IPCW(Cox) super learner and the state
learner approaches the benchmark provided by the oracle selector for large sample
sizes.
\begin{figure}
  \centerline{\includegraphics[width=1\linewidth]{../figures/zelefski-sim.pdf}}
  \caption[]{Results for scenario~2 of the simulation study. For the learner
    selected by each of the four discrete super learners, the Brier score
    calculated in a large independent data set without censoring is plotted
    against sample size. The results are based on 200 repetitions.}
  \label{fig:zelefski}
\end{figure}

\section{Case study: Bystander efforts in out-of-hospital cardiac arrest}
\label{sec:case-study:-byst}

@@

\begin{figure}
  \centerline{\includegraphics[width=1\linewidth]{../figures/zelefski-real-data.pdf}}
  \caption[]{The results of applying the 125 combinations of learners to the
    prostate cancer data set. The learners are \texttt{KM} (KM), \texttt{Cox
      strata CS} (strata), \texttt{Lasso} (lasso), \texttt{Elastic} (elastic),
    and \texttt{RF} (RF) as described Table~\ref{tab:zel-library}. The error
    bars are based on five repetitions using different splits. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Death learner', and `Censoring learner', respectively.}
  \label{fig:zelefski-real}
\end{figure}

\begin{table}[ht]
  \centering \input{../figures/zel-tab.tex}
  \caption{The 10 best performing models in terms of integrated Brier score. The
    reported standard errors are based on five repetitions using different
    splits. The models are described in Table~\ref{tab:zel-library}. We refer to
    learners of \( \Lambda_1 \), \( \Lambda_2 \), and $\Gamma$ as `Tumor
    learner', `Death leaner', and `Censoring learner', respectively.}
  \label{tab:zelefski-real}
\end{table}
\section{Discussion}
\label{sec:discussion}
